#Regression Report 
<br />
*`r input$name`* <br />   
*`r as.character(format(Sys.Date(), format="%B %d, %Y"))`*

<br />

###1. Summary Statistics

This report was created using the `r input$dataset` data set.  The dependent variable in my analysis is `r input$dv` and independent variable in my analysis is `r input$iv`. 

<br />

The summary statistics of `r input$dv` and `r input$iv` appear below. 
```{r summary, echo=FALSE}
  mlb11 <- datasetInput()
  temp <- cbind(mlb11[input$dv], mlb11[input$iv])
  summary(temp)
```

`r input$text_summary` 

<br />

###2. Histograms

The histograms of `r input$dv` and `r input$iv` appear below. <br />
<br />
<br />

```{r hist_dv, echo=FALSE}
    x    <- mlb11[,input$dv]  
    bins <- seq(min(x), max(x), length.out = input$bins_dv + 1)
    
    hist(x, breaks = bins, col = 'darkgray', border = 'white', main = 'Dependent Variable', xlab = input$dv)
```

`r input$text_hist_dv`

```{r hist_iv, echo=FALSE}
    x    <- mlb11[,input$iv]  
    bins <- seq(min(x), max(x), length.out = input$bins_iv + 1)
    
    hist(x, breaks = bins, col = 'darkgray', border = 'white', main = 'Independent Variable', xlab = input$iv)
```

`r input$text_hist_iv`

<br />

###3. Scatter Plot 

A scatter plot of `r input$dv` and `r input$iv` appears below.  <br />
<br />

```{r scatter, echo=FALSE}

  plot(mlb11[,input$iv], mlb11[,input$dv],
       xlab = input$iv, ylab = input$dv,  main = "Scatter Plot of Independent and Dependent Variables", pch = 16, 
       col = "black", cex = 1) 
  
  abline(lm(mlb11[,input$dv]~mlb11[,input$iv]), col="grey", lwd = 2) 
```

`r input$text_scatter`

<br />

###4. Correlations

A correlation matrix of all of the variables in `r input$dataset` appears below. 
```{r correlation, echo=FALSE}

cor <- as.data.frame(cor(mlb11[,-1]))
cor <- format(round(cor, 2), nsmall = 2)
cor

```

`r input$text_correlation`

<br />

###5. Regression Model

A bivariate regression model predicting `r input$dv` with `r input$iv` appears below. 

```{r model, collapse=TRUE, echo=FALSE}
options(digits = 4)

m1 <- lm(regFormula(), data = mlb11)
b <- coef(m1)
summary(m1)
```

The fitting result is $`r input$dv` = `r b[1]` + `r b[2]``r input$iv`$. <br />

`r input$text_model`

<br />


###6. Residuals

```{r residuals_hist, collapse=TRUE, echo=FALSE}

hist(model()$residuals, main = paste(input$dv, '~', input$iv), xlab = 'Residuals') 

```

```{r residuals_scatter, collapse=TRUE, echo=FALSE}

  plot(model()$residuals ~ mlb11[,input$iv], xlab = input$iv, ylab = 'Residuals')
  abline(h = 0, lty = 3) 
```

```{r residuals_qqline, collapse=TRUE, echo=FALSE}

  qqnorm(model()$residuals)
  qqline(model()$residuals) 
```


`r input$text_residuals`








